Технология использования открытых данных Федеральной налоговой службы России для экономико-географического анализа

### 2024-04-16 legal-companies-geography/Paper.Rmd
Write methods, #1

*Second,* the filter-on-extract approach was used to extract necessary information from the raw archives into intermediary CSV tables. The filter-on-extract approach means that instead of unpacking the entire archive on the disk, the program reads its contents file by file without unpacking, parses the internal XML structure, extracts necessary attributes only, filters the records by activity code to leave legal companies only, and stores the result on the disk. Thus, the runtime and disk usage are substantially reduced compared to the traditional extract-then-filter method.

@@

*Fifth,* the data on business entities was combined with the data on employees using taxpayer ID as unique identifier common to both datasets, and also converted into a panel time series table that includes yearly information for each company or individual.

>>>>

*Second,* the filter-on-extract approach was used to extract necessary information from the raw archives into intermediary CSV tables. The filter-on-extract approach means that instead of unpacking the entire archive on the disk, the program reads its contents file by file without unpacking, parses the internal XML structure, extracts necessary attributes only, filters the records by activity code equal to 69.10 to leave legal companies only, and stores the result on the disk. Thus, the runtime and disk usage are substantially reduced compared to the traditional extract-then-filter method.

@@

*Fifth,* the data on business entities was combined with the data on employees using taxpayer ID as unique identifier common to both datasets, and also converted into a panel time series table that includes yearly information for each company or individual. This resulting table is used in the further analysis.

The research follows the general framework of regional analysis and uses the methods of descriptive statistics and data visualization, including the plotting of data on a tile-grid map of Russia. The analysis consists of a few research problems, or questions, that are listed below with the description of the relevant techniques used to find answers to them.

The first problem is the *distribution of legal firms by regions* of Russia. To answer this question, legal firms that existed in 2021 are counted by the region, and the result is visualized on the map.

The second problem is the *structure of legal business in regions* with respect to the kind of firms (either individual entrepreneurs or organisations) and the size of organisations (either micro, small, and medium). To answer this question, legal firms are counted by region, kind and type, and the result is visualized on a geofacetted plot.

The third problem is the *role of legal business on the regional and national scale*, that is, either its importance within a given region or the importance of region's legal services in the Russia's legal market. To discover this issue, two calculations are made. The first one is used to better understand the role of the region in the country's legal business and is done by calculating the share of legal companies employees of a region in the total number of country's legal companies employees. The second one is aimed at estimating the relative role of legal business in region's economy and is done by dividing the number of legal companies employees in a region by the total number of employees in a region. Both two metrics are then plotted on a tile-grid map.

The fourth issue deals with the temporal dimension and reflects the *change of the number of legal firms* in the regions. Legal firms are calculated by region and year, and the results are plotted.

Several aspects are common to all the questions. First of all, despite the presence of data from 2016 to 2024, only a part from 2016 to 2021 inclusively is utilized for the analysis. The reason for this is the Russia's military operation in Ukraine and the subsequent structural transformation of the economy, international sanctions, substantial political and legal changes in the country that may have significantly impacted the legal market compared to the previous period, and even though all these changes could have been interesting to study, the purpose of the current research is to draw an overall picture of legal market in Russia in “normal situation” without any serious perturbations. Statistics for several consequent years, if not processed separately (e. g. in the case of temporal changes), is averaged using median as a function (e.g. number of legal firms for 2016–2021 in the region is the median of counts for each year from 2016 to 2021). Next, both organisations and individual entrepreneurs are accounted for. If statistical computations require the count of employees, it is assumed that an individual entrepreneur always has exactly one employee, that is, this person itself. This is because even though individual entrepreneurs in Russia can legally employ people, the corresponding information is not available in the FTS open data possibly due to personal data protection issues. Also, if an organisation has reported zero count of employees, it is still assumed that is has exactly one employee, that is, the company's owner itself.
